\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2016-12-15 manuscript.tex
Change citation to use Dr. Lee's document
Modify er_dot proposition to include bound on A(R)

\begin{prop}[Bound on \( \bm{\dot{e}_R} \)]\label{prop:eR_dot_bound}
Consider a domain \( D \) about the desired attitude defined as
\begin{align}
	D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}. \label{eqn:domain}
\end{align}
Then the following statements hold:
\begin{enumerate}[(i)]
	\item \label{item:prop_eR_dot_bound_AB} Upper bounds of \( A(R) \) and \( B(R) \) are given by
	\begin{gather}
		\norm{A} < c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
	\end{gather}
	\item \label{item:prop_eR_dot_bound_EF} Upper bounds of \( E(R,R_d) \) and \( F(R) \) are given by
	\begin{gather}
		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G}  , \label{eqn:E_bound} \\
		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^2 \parenth{\beta^2-2}}{\alpha^2 \parenth{\beta-\cos \theta}^4} . \label{eqn:F_bound}
	\end{gather}
	\item Upper bounds of the attitude error vectors \( e_{R_A} \) and \( e_{R_B} \) are given by
	\begin{gather}
		\norm{e_{R_A}} \leq \sqrt{\frac{\psi}{b_1}}, \label{eqn:eRA_bound} \\
		\norm{e_{R_B}} \leq \frac{\sin\theta}{\alpha \parenth{\cos \theta - \beta}}. \label{eqn:eRB_bound}
	\end{gather}
\end{enumerate}
These results are combined to yield a maximum upper bound of the time derivative of the attitude error vector \( \dot{e}_R \) as
\begin{gather}
	\norm{\dot{e}_R} \leq H \norm{e_\Omega} ,\label{eqn:eR_bound}
\end{gather}
where  \( H \in \R \) is defined as
\begin{gather}
	H = \norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}. \label{eqn:H}
\end{gather}
\end{prop}
\begin{proof}
See~\Cref{proof:eR_dot_bound}
\end{proof}

@@

The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{lee2013b,ioannou2012}. 
A wide variety of realistic disturbances, such as gravitational gradients or malfunctioning thrusters, are accurately represented via this model. 
In addition, it is possible to represent the uncertainty of a time-varying inertia matrix as an equivalent external disturbance. 
For example, Euler's law gives the relationship for the rate of change of angular momentum
\begin{align*}
    M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
\end{align*}
Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment.
Finally, it has been shown that this adaptive control formulation is able to handle time-varying disturbances under some mild assumptions~\cite{ioannou2012}.

@@

\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
%	We know that \( B \to \infty \) as the constraint is neared. 
%	We assume that \( B > \psi \) which implies that \( A < 1 \).
%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
Therefore, the selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.

>>>>

\begin{prop}[Bound on \( \bm{\dot{e}_R} \)]\label{prop:eR_dot_bound}
Consider a domain \( D \) about the desired attitude defined as
\begin{align}
	D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}. \label{eqn:domain}
\end{align}
Then the following statements hold:
\begin{enumerate}[(i)]
	\item \label{item:prop_eR_dot_bound_AB} Upper bounds of \( A(R) \) and \( B(R) \) are given by
	\begin{gather}
		\norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
	\end{gather}
  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
  \begin{align*}
    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
  \end{align*}
	\item \label{item:prop_eR_dot_bound_EF} Upper bounds of \( E(R,R_d) \) and \( F(R) \) are given by
	\begin{gather}
		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G}  , \label{eqn:E_bound} \\
		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^2 \parenth{\beta^2-2}}{\alpha^2 \parenth{\beta-\cos \theta}^4} . \label{eqn:F_bound}
	\end{gather}
	\item Upper bounds of the attitude error vectors \( e_{R_A} \) and \( e_{R_B} \) are given by
	\begin{gather}
		\norm{e_{R_A}} \leq \sqrt{\frac{\psi}{b_1}}, \label{eqn:eRA_bound} \\
		\norm{e_{R_B}} \leq \frac{\sin\theta}{\alpha \parenth{\cos \theta - \beta}}. \label{eqn:eRB_bound}
	\end{gather}

\end{enumerate}
These results are combined to yield a maximum upper bound of the time derivative of the attitude error vector \( \dot{e}_R \) as
\begin{gather}
	\norm{\dot{e}_R} \leq H \norm{e_\Omega} ,\label{eqn:eR_bound}
\end{gather}
where  \( H \in \R \) is defined as
\begin{gather}
	H = \norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}. \label{eqn:H}
\end{gather}
\end{prop}
\begin{proof}
See~\Cref{proof:eR_dot_bound}
\end{proof}

@@

The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{LeeITCST13,ioannou2012}. 
A wide variety of realistic disturbances, such as gravitational gradients or malfunctioning thrusters, are accurately represented via this model. 
In addition, it is possible to represent the uncertainty of a time-varying inertia matrix as an equivalent external disturbance. 
For example, Euler's law gives the relationship for the rate of change of angular momentum
\begin{align*}
    M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
\end{align*}
Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment.
Finally, it has been shown that this adaptive control formulation is able to handle time-varying disturbances under some mild assumptions~\cite{ioannou2012}.

@@

\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
%	We know that \( B \to \infty \) as the constraint is neared. 
%	We assume that \( B > \psi \) which implies that \( A < 1 \).
%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
